A North Sámi to South Sámi machine translation prototype

### 2014-02-05 paper/paper.tex
Some possible points.

\section{Introduction}

>>>>

\section{Introduction}
Suggestions from Lene:  
\begin{enumerate}
\item main point: 
\begin{itemize}
\item translation nob-sma which actually is nob-sme-sma (should somehow be in the title?) 
\item the evaluators evaluate nob-sma
\end{itemize}
\item subpoints: 
\begin{itemize}
\item larger syntactic differences between SL an TL than usually done in Apertium?
\item little sma lexical resources, we have to find words by comparing translated texts
\item reaction from sma linguist in the normgiving organ: she sees the possibility of using MT as a help for discussing terminology and getting the best ones into use
\item the language socity is used to the impact from the mojority languages, a new controversial(?) thought is the linguistic impact from another minority lanugage 
\end{itemize}
\end{enumerate}
